---
title: "Simple document"
output: github_document
---

```{r, echo =FALSE, message = FALSE}
library(tidyverse)
library(readxl)
```

## Import some data

I want to import "FAS_litters.csv"

```{r}
litters_df = read_csv("data/FAS_litters.csv")

#read_csv("/Users/")绝对路径
```

I import the dataset. Now I want better names.

```{r}
names(litters_df)

litters_df = janitor::clean_names(litters_df)#不需要引入package
```

Now I have better names. Let's look at dataset.

```{r}
litters_df

head(litters_df)
tail(litters_df)
```

One I use a lot is:
```{r, evol = FALSE}
view(litters_df)
```

Here is "skimr"

```{r}
skimr::skim(litters_df)
```


## Argument in "read_csv"

```{r}
litters_df = read_csv(
  "data/FAS_litters.csv",
  skip = 5,
  col_names = FALSE,
  na = "Low8"
)
```

##Parsing columns

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
```


## Reading from Excel
```{r}
mlb11_data = read_excel("data/mlb11.xlsx")
```

LotR Words is next

```{r}
fellow_df = read_excel("data/LotR_words.xlsx", range = "B3:D6")
```


## Read a SAS file 

this is where I wanted to read sas but didn't 

```{r}
pluse_df = read_sas("data/public_pulse_data.sas7bdat")
```

## why use `read.csv`

`read.csv` doesn't give `tibble` and that's really bad
```{r}
litters_df_base = read.csv("data/FAS_litters.csv")
```

## how do I export data

there is 

```{r}
write_csv(fellow_df, "data/template.csv")
```

